---
title: "Homework 5"
author: "Amelia Zhao"
date: '`r format(Sys.time(), "%Y-%m-%d")`'
output: github_document

---

```{r global_options, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
```

# Problem 1

```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(mgcv)
library(modelr)
library(purrr)

```


```{r}

"./data"

birthweight <-
  list.files(path = "./data", full.names = TRUE) %>% 
  map(read.csv) %>% 
  reduce(rbind) %>% 
  mutate(
      babysex = factor(babysex),
      frace = factor(frace),
      malform = factor(malform),
      mrace = factor(mrace)
  )

sum(is.na(birthweight))

```

In my regression model for birthweight, I chose variables that are clinically relevant, and that women may be interested in knowing about. 
For example, SES status is known to affect innumerous health outcomes. I'm interested in maternal health, specifically in examining the effect of a pregnant mother's actions and prenatal health on post-natal physiological outcomes. Thus, I've chosen variables that are related to the mother's prenatal health. 
```{r}

mymodel = lm(bwt ~ delwt + fincome + gaweeks + menarche + momage + parity + pnumlbw + ppbmi + smoken + wtgain, data = birthweight)
mymodel %>% 
  broom::tidy() %>% 
  knitr::kable()
mymodel %>% 
  broom::glance() %>% 
  knitr::kable()

birthweight %>% 
  modelr::add_predictions(mymodel) %>% 
  modelr::add_residuals(mymodel) %>% 
  ggplot(aes(x = pred , y = resid)) + geom_point(alpha = 0.5, color = "darkgreen") +
  geom_hline(yintercept = 0, color = "darkblue") + 
  labs(title = "Figure 1. Residuals and Predicted Value of Birthweight", 
       x = "Predicted birthweight (grams)", 
       y = "Residuals")

```

Comparison of my model to one using length at birth and gestational age (Figure 2, Model 2), and one using head circumference, length, sex, and all interactions thereof (Figure 2, Model 3). 

```{r}

comp1 = lm(bwt ~ blength + gaweeks, data = birthweight)
comp1 %>% 
  broom::tidy() %>% 
  knitr::kable()
comp1 %>% 
  broom::glance() %>% 
  knitr::kable()

comp2 = lm(bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = birthweight)
comp2 %>% 
  broom::tidy() %>% 
  knitr::kable()
comp2 %>% 
  broom::glance() %>% 
  knitr::kable()



cv_df <- 
  crossv_mc(birthweight, 100) %>% 
  mutate(train = map(train, as_tibble),
         test = map(test, as_tibble)
         ) %>% 
  mutate(
    mymodel = map(train, ~lm(bwt ~ delwt + fincome + gaweeks + menarche + momage + parity + pnumlbw + ppbmi + smoken + wtgain, data = .x)), 
         comp1 = map(train, ~lm(bwt ~ blength + gaweeks, data = .x)),
         comp2 = map(train, ~lm( bwt ~ babysex + bhead + blength + babysex*bhead + babysex*blength + bhead*blength + babysex*bhead*blength, data = .x))) %>%
  mutate(rmse_mymodel = map2_dbl(mymodel, test, ~rmse(model = .x, data = .y)),
         rmse_comp1 = map2_dbl(comp1, test, ~rmse(model = .x, data = .y)),
         rmse_comp2 = map2_dbl(comp2, test, ~rmse(model = .x, data = .y)))

cv_df %>% 
	select(starts_with("rmse")) %>% 
	gather(key = model, value = rmse) %>%
	mutate(model = recode(model, "rmse_mymodel" = "My Model",
												"rmse_comp1" = "Model 2",
												"rmse_comp2" = "Model 3")) %>%
	ggplot(aes(x = model, y = rmse)) +
	  geom_boxplot() +
		labs(
		  title = "Figure 2. Models and RMSE",
			x = "Model",
			y = "Residual Mean Squared Error"
		)

```

## Models

As shown in Figure 2, my maternal-focused model is high in prediction error, the highest of the three models. Although there is no test and thus no statistical significance, my model clearly has a much higher RMSE than the other models. This model should not be used to predict birthweight. 


# Problem 2

```{r}

weather = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(id, USW00094728 = "CentralPark_NY"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())

```


```{r}
boot_sample = function(df) {
  sample_frac(df, replace = TRUE)
}
boot_straps = 
  tibble(
    strap_number = 1:5000,
    strap_sample = rerun(5000, boot_sample(weather))
  )


results <-
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data=.x)),
    results = map(models, broom::tidy)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(cols = c(results)) %>% 
  select(strap_number, term, estimate) %>% 
  pivot_wider(
    names_from = "term",
    values_from = "estimate"
  ) %>% 
  janitor::clean_names() %>% 
  mutate(log = log(intercept*tmin)) 


results2 <-
  boot_straps %>% 
  mutate(
    models = map(strap_sample, ~lm(tmax ~ tmin, data = .x)),
    results = map(models, broom::glance)) %>% 
  select(-strap_sample, -models) %>% 
  unnest(cols = c(results))



plotdata <-
  ggplot(
    data = results, aes(x = log)) + geom_histogram() + 
  labs(
    title = "Figure 3. Distribution of Log(beta0*beta1) Estimates",
    x = "Log Beta0*Beta1",
    y = "Count"
    ) 

plotdata

plotdata2 <-
  ggplot(data = results2, aes(x = r.squared)) + geom_histogram() + 
  labs(
    title = "Figure 4. Distribution of R Squared Estimates",
    x = "R Squared",
    y = "Count"
    ) 

plotdata2

```

Shown in Figures 3 and 4, the plots of the estimates of beta0*beta1 and R squared are relatively normal. The R squared plot may be slightly skewed right, but is mostly normal. 


```{r}

quantile(pull(results, log), probs = c(0.025, 0.975)) 
quantile(pull(results2, r.squared), probs = c(0.025, 0.975)) 

```

log(b0*b1) 95% Confidence Interval: 1.965, 2.059

R squared 95% Confidence Interval: 0.894, 0.927
